Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-22 ApproximateCode.tex
version 4.2

\author{Huayi Jin}
\email{keplar_gd@sjtu.edu.cn}
\affiliation{%
  \institution{Shanghai Jiao Tong University}
}

\author{Chentao Wu}
\author{Xin Xie}
\author{Jie Li}
\author{Minyi Guo}
\affiliation{
  \institution{Shanghai Jiao Tong University}
}

\author{Hao Lin}
\author{Jianfeng Zhang}
\authornotemark[1]
\affiliation{%
  \institution{The Alibaba Group}
}

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering\small
\begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
\hline
Symbols & \multicolumn{1}{c|}{Description} \\ \hline \hline
$k$ & the number of data nodes in a local stripe \\ \hline
$r$ & the number of local parity nodes in a local stripe \\ \hline
$n$ & the number of all data and parity nodes in a local stripe ($n=k+r$) \\ \hline
$h$ & the number of local stripes to construct a global stripe \\ \hline
$g$ & the number of global parity nodes \\ \hline
$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline
$D_i$ & data nodes \\ \hline
$P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
$P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data in a video file \\ \hline
UD & unimportant data in a video file \\ \hline
\end{tabular}
\end{table}

@@

Reed Solomon Code \cite{RS} (RS code) is one kind of classic MDS codes, but its scheme requires additions and multiplications over finite fields and results in high complexity in decoding and updating. Several attempts have been made to address this issue.

\textcolor{red}{Need to update}
Local Construction Code (LRC) \cite{LRC} divides the data nodes into multiple local groups, each with a local parity node, and the global parity is calculated by all data nodes. Therefore, when a single node is corrupted, data can be recovered by local parity without requiring access to all nodes.
LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{LRC}.

\begin{figure}
    \centering
    \includegraphics[height=2.5cm]{photo/LRC.pdf}
    \caption{LRC}
\end{figure}

@@

\subsection{Approximate Storage}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced.
Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

\begin{table}[ht]
\centering
\caption{
\textcolor{red}{Need to update}
Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
\small
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5}
 & RAID-6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Approximate Storage} & low & low & high \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5}
 & UD &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

%Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
%First, the overhead of existing 3DFTs erasure codes is too high.
Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

@@

@@

\subfigure[Generation of local parities]{
    \label{fig-ap-tip-lP}
    \includegraphics[width = 0.59\linewidth]{photo/APPR-STAR-LO.pdf}
}
\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.35\linewidth]{photo/APPR-STAR-GL.pdf}
}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
\label{fig-ap-5214}
\end{figure}

@@

\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.75\linewidth]{photo/APPR-TIP-GL.pdf}
}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
\label{fig-ap-TIP}
\end{figure}

@@

\begin{figure*}[ht]
\subfigure[APPR.STAR and STAR]{
    \label{fig-encodingSTAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-Star.eps}
}
\subfigure[APPR.TIP and TIP]{
    \label{fig-encodingTIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-TIP.eps}
}
\subfigure[APPR.TIP/STAR and RS]{
    \label{fig-encodingRS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-RS.eps}
}
\subfigure[APPR.TIP/STAR and LRC]{
    \label{fig-encodingLRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-LRC.eps}
}
\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
\end{figure*}

\begin{figure*}[ht]
\subfigure[APPR.STAR and STAR]{
    \label{fig-decoding-1-STAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-Star.eps}
}
\subfigure[APPR.TIP and TIP]{
    \label{fig-decoding-1-TIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-TIP.eps}
}
\subfigure[APPR.TIP/STAR and RS]{
    \label{fig-decoding-1-RS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-RS.eps}
}
\subfigure[APPR.TIP/STAR and LRC]{
    \label{fig-decoding-1-LRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-LRC.eps}
}
\caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
\end{figure*}

\begin{figure*}[ht]
\subfigure[AP and RS]{
    \label{fig-decoding-2-STAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-Star.eps}
}
\subfigure[AP and STAR]{
    \label{fig-decoding-2-TIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-TIP.eps}
}
\subfigure[AP and TIP]{
    \label{fig-decoding-2-RS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-RS.eps}
}
\subfigure[APPR.TIP/STAR and LRC]{
    \label{fig-decoding-2-LRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-LRC.eps}
}
\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
\end{figure*}

\begin{figure*}[ht]
    \subfigure[AP and RS]{
        \label{fig-decoding-3-STAR}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-Star.eps}
    }
    \subfigure[AP and STAR]{
        \label{fig-decoding-3-TIP}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-TIP.eps}
    }
    \subfigure[AP and TIP]{
        \label{fig-decoding-3-RS}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-RS.eps}
    }
    \subfigure[APPR.TIP/STAR and LRC]{
        \label{fig-decoding-3-LRC}
        \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-LRC.eps}
    }
    \caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
    \end{figure*}

@@

@@

\begin{acks}

\end{acks}

>>>>

\author{Huayi Jin, Chentao Wu, Xin Xie, Jie Li, Minyi Guo, Hao Lin, Jianfeng Zhang}
%\email{keplar_gd@sjtu.edu.cn}
\affiliation{%
  \institution{Shanghai Jiao Tong University}
}

\author{Hao Lin, Jianfeng Zhang}
\authornotemark[1]
\affiliation{%
  \institution{The Alibaba Group}
}

@@

\begin{table}[]\footnotesize
\caption{The symbols used in this paper.}\label{parameter}
\centering
\begin{tabular}{|p{0.7cm}<{\centering}|p{6.5cm}|}
\hline
Symbols & \multicolumn{1}{c|}{Description} \\ \hline \hline
$k$ & the number of data nodes in a local stripe \\ \hline
$r$ & the number of local parity nodes in a local stripe \\ \hline
$n$ & the number of all data and parity nodes in a local stripe. ($n=k+r$) \\ \hline
$h$ & the number of local stripes to construct a global stripe \\ \hline
$g$ & the number of global parity nodes \\ \hline
$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
$E_{i,j}$ & the element at the $i$-th row and $j$-th column \\ \hline
$D_i$ & a data node \\ \hline
$P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
$P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
$\oplus$ & the XOR operation symbol \\ \hline
$\binom{n}{k}$ & The number of $k$-combinations from $n$ elements\\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data in a video file \\ \hline
UD & unimportant data in a video file \\ \hline
\end{tabular}
\end{table}

@@

Reed Solomon Code \cite{RS} (RS code) is a classic MDS code. The encoding and decoding operations of RS code are based on Galois Field (GF), leading to high scalability as well as high computational complexity. All the parities of RS code are horizontal as shown in Figure \ref{fig-RS-1}.

\textcolor{red}{Need to update}
Local Construction Code (LRC) \cite{LRC} divides the data nodes into multiple local groups, each with a local parity node, and the global parity is calculated by all data nodes. Therefore, when a single node is corrupted, data can be recovered by local parity without requiring access to all nodes.
LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{fig-LRC-1}.

\begin{figure}
    \centering
    \subfigure[\textbf{RS Code:} Horizontal parity coding (e.g., $E_{0,5} = \sum_{i=0}^3 A_{0,i}E_{0,i}$)]{
        \includegraphics[width=0.26\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
    }
    \hspace{3px}
    \subfigure[\textbf{LRC Code:} Horizontal parity coding (e.g., the local parity $E_{0,5} = \sum_{i=2}^3 A_{0,i}E_{0,i}$ and the global parity $E_{0,7} = \sum_{i=0}^3 A_{0,i}E_{0,i}$)]{
        \includegraphics[width=0.67\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
    }
    \caption{Encoding of RS code and LRC}
\end{figure}

@@

\subsection{Approximate Storage \textcolor[rgb]{1.00,0.00,0.00}{Compression}}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced.
Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

\begin{table}[ht]\footnotesize
\centering
\caption{
Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|}
\hline
\multirow{2}{*}{EC} & RS & high & high & high \\ \cline{2-5}
 & RAID-6 & medium & medium & medium \\ \hline
\multicolumn{2}{|c|}{Approximate Storage} & low & low & low \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate\\ Code\end{tabular}} & ID & low & high & low \\ \cline{2-5}
 & UD & low & medium & low \\ \hline
\multicolumn{2}{|c|}{Data Compression} & low & / & high \\ \hline
\end{tabular}
\end{table}

@@

%Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.
%First, the overhead of existing 3DFTs erasure codes is too high.
%Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
%Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=0.9\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

@@

\begin{figure}
    \centering
    \subfigure[XXX]{
        \includegraphics[width=0.26\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
    }
    \subfigure[XXX]{
        \includegraphics[width=0.68\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
    }
    \caption{XXXX}
\end{figure}

@@

\subfigure[Generation process]{
    \label{fig-ap-tip-GEN}
    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
\label{fig-ap-5214}
\end{figure}

@@

\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.8\linewidth]{photo/APPR-TIP-GL-v2.pdf}
}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP code is defined as the global parity nodes in this case.}
\label{fig-ap-TIP}
\end{figure}

@@

\begin{figure*}[ht]
\subfigure[APPR.STAR and STAR]{
    \label{fig-encodingSTAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-Star.eps}
}
\subfigure[APPR.TIP and TIP]{
    \label{fig-encodingTIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-TIP.eps}
}
\subfigure[APPR.TIP/STAR and RS]{
    \label{fig-encodingRS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-RS.eps}
}
\subfigure[APPR.TIP/STAR and LRC]{
    \label{fig-encodingLRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Encoding-LRC.eps}
}\vspace{-0.5cm}
\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
\end{figure*}

\begin{figure*}[ht]
\subfigure{
    \label{fig-decoding-1-STAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-Star.eps}
}
\subfigure{
    \label{fig-decoding-1-TIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-TIP.eps}
}
\subfigure{
    \label{fig-decoding-1-RS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-RS.eps}
}
\subfigure{
    \label{fig-decoding-1-LRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-1-LRC.eps}
}\vspace{-0.5cm}
\caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
\end{figure*}

\begin{figure*}[ht]
\subfigure{
    \label{fig-decoding-2-STAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-Star.eps}
}
\subfigure{
    \label{fig-decoding-2-TIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-TIP.eps}
}
\subfigure{
    \label{fig-decoding-2-RS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-RS.eps}
}
\subfigure{
    \label{fig-decoding-2-LRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-2-LRC.eps}
}\vspace{-0.5cm}
\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
\end{figure*}

\begin{figure*}[ht]
\subfigure{
    \label{fig-decoding-3-STAR}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-Star.eps}
}
\subfigure{
    \label{fig-decoding-3-TIP}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-TIP.eps}
}
\subfigure{
    \label{fig-decoding-3-RS}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-RS.eps}
}
\subfigure{
    \label{fig-decoding-3-LRC}
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Decoding-3-LRC.eps}
}\vspace{-0.5cm}
\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-3}
\end{figure*}

@@

\iffalse
\begin{figure}[ht]
\centering
\subfigure[]{
\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-2.eps}\label{fig-rec-2}
}\hspace{-0.4cm}
\subfigure[]{
\includegraphics[width=0.5\linewidth]{photo/experiment/Recovery-3.eps}\label{fig-rec-3}
}
\caption{Recovery time Result using Frame Interpolation}
\label{fig-recoverytime}
\end{figure}
\fi

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{photo/experiment/Recovery-2-3.pdf}\label{fig-rec-3}
\caption{Recovery time Result using Frame Interpolation}
\label{fig-recoverytime}
\end{figure}

@@
